### 2014-06-10 analysis/network_properties.Rmd
network properties fixed, analysis divided between k=1:5 and k = 10..50

Context Permeability Investigations
===================================
We now investigate the first variation of the multi-network simulation model we called _Context Permeability_.
We first investigate how different network topologies affect the convergence to consensus.  We change the network 
models and the number of networks in which each agent interacts. Obviously, in this mode, adding more networks means
adding more connections. We show that what is important is not the number of connections but rather the properties they 
display when they are merged.

# Convergence to Consensus with Regular Networks #
We first investigate how the convergence is affected by regular networks. We use a _K-Regular_ network model 
in which each agent has the same number of connections. The number of connections is controlled by parameter _k_. Each agent has _2*k_ connections. This structure is not very realistic if we compare it with real network structures. Nonetheless, this investigation is useful for two reasons. The first is that we can investigate the influence of connectivity in the convergence to consensus. The second is that these models of interaction can be used outside the 
social simulation domain, nothing prohibits multi-agent systems to use these as models of interaction, we might even want to construct highly clustered networks of agents. Given this, it is valuable to know how the system responds to such structures.

@@

In this first experiment we performed experiment with _k-regular_ networks with different _k_ values. We also varied the number of concomitant networks as follows:

@@

First, we load the network data from the regular network experiment. 
This is somehow a large file so we use the `bigmemory` package which 
is more efficient in terms of memory management.
```{r message=FALSE}
source("../R/network.utils.R")
require(bigmemory)
network_data <- read.big.matrix(filename="../data/regular_networks/networks.csv", header=T, sep=";")
```

@@

#create box plots
net_props <- props[props$networks > 2,]

@@

net_props <- props[props$networks > 0,]

@@

#plot average path length
net_props <- average_apl_data

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",))

plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)

plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)

plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
plot

@@

```{r}
#lets plot the clustering coefficient
net_props <- average_clustering_data

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",))

plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)

plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)

plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
plot

>>>>

Context Permeability Investigations: Network Properties
=======================================================
We now investigate the first variation of the multi-network simulation model we called _Context Permeability_.
We first investigate the properties of different network topologies that we then use in our model. We change the network 
models and the number of networks in which each agent interacts. Obviously, adding more networks means
adding more connections. We show that what is important is not exactly the number of connections but rather the properties the 
networks display when they are merged.

# Properties for K-Regular Networks #
We first investigate the properties of regular networks. We use a _K-Regular_ network model 
in which each node has the same number of connections. The number of connections is controlled by parameter _k_. Each agent has _2*k_ connections. This structure is not very realistic if we compare it with real network structures. Nonetheless, this investigation is useful for two reasons. The first is that we can investigate the influence of connectivity in the convergence to consensus. The second is that these models of interaction can be used outside the social simulation domain, nothing prohibits multi-agent systems to use these as models of interaction, we might even want to construct highly clustered networks of agents. Given this, it is valuable to know how the system responds to such structures.

@@

In a first experiment we performed experiment with _k-regular_ networks with different _k_ values. We also varied the number of concomitant networks as follows:

@@

We load the network data from the regular networks experiment with the `bigmemory` package which 
is more efficient in terms of memory management.
```{r message=FALSE}
source("../R/network.utils.R")
require(bigmemory)
network_data <- read.big.matrix(filename="../data/regular_networks/networks.csv", header=T, sep=";")
```

@@

#create average path length box plots for k = 1,2,3,4,5
net_props <- props[props$k <= 5,]

@@

#create average path length box plots for k = 10, 20,30,40,50
net_props <- props[props$k > 5,]

#create clustering coefficient box plots for k = 1,2,3,4,5
net_props <- props[props$k <= 5,]

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$k)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="K", y="Clustering Coefficient", x="Number of Networks")
plot

#create clustering coefficient box plots for k = 10,20,30,40,50
net_props <- props[props$k > 5,]

@@

#plot average path length for k = 1,2,3,4,5
net_props <- average_apl_data[average_apl_data$"k" <= 5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
plot

#plot for k = 10,20,30,40,50
net_props <- average_apl_data[average_apl_data$"k" >5,]
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Average Path Length", x="Number of Networks")
plot

@@

```{r}
#plot for k = 1,2,3,4,5
net_props <- average_clustering_data[average_clustering_data$"k" <= 5, ]

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
plot

#plot for k = 10,20,30,40,50
net_props <- average_clustering_data[average_clustering_data$"k" > 5, ]

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$k), color=as.factor(net_props$k)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$k), group=as.factor(net_props$k), linetype=as.factor(net_props$k)),size=1)   
plot <- plot + labs(color="K", shape="K", linetype="K", y="Clustering Coefficient", x="Number of Networks")
plot
